---
title: "Course Project : Shiny Application and Reproducible Pitch"
author: "Tan Siu Ching"
date: "2025-04-25"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown of the Air Quality Explorer
This is an R Markdown presentation document is created as part of the TSC Course Project. The goal of this project is to develop a Shiny web application using the built-in airquality dataset, and to present its functionality through a reproducible pitch presentation. 

The application enables users to explore key air quality metrics recorded in New York during the summer of 1973, providing interactive visualizations and summary statistics to support data-driven insights.

## **Why This App?**

- Leverages `airquality` dataset in base R
- Designed for beginner-friendly interactive use
- Focused on simplicity, minimal setup

### **App Features**

- Selectable variables (e.g., Ozone, Temp, Wind)
- Interactive histogram with custom bin size
- Real-time summary statistics

## About the Data 
```r
summary(airquality$Ozone)
hist(airquality$Ozone, breaks = 10)
```
```{r}
summary(airquality$Ozone)
hist(airquality$Ozone, breaks = 10)
```

## About This Project: Shiny Application & Pitch Presentation. Try It Out!

Explore the complete Shiny application developed for this project by clicking the link below:

[🔗 View Shiny App](https://sctan.shinyapps.io/Course_Project_Shiny_Application_and_Reproducible_Pitch/)

https://sctan.shinyapps.io/Course_Project_Shiny_Application_and_Reproducible_Pitch/

Access the full project files, including source code and documentation, on GitHub:

[💻 View GitHub Repository](https://github.com/SCTAN-Msia/Course_Project_Shiny_Application_and_Reproducible_Pitch)

https://github.com/SCTAN-Msia/Course_Project_Shiny_Application_and_Reproducible_Pitch

Simple, insightful, and ready to explore!

